---
title: "StatsReport"
author: "lushi"
date: "17/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Selection Process

```{r data, include=FALSE}
#path = "/Users/lucia/phd_work/cognitive_distortion/data/"
path = "/home/lucia/phd_work/mypersonality_data/cognitive_distortion/data/"
setwd(path)
dep <- read.csv('dep.csv')
dep_status <- read.csv('user_status_match_dep.csv')
demog <- read.csv('demog.csv')
```


```{r}
#matching depression, status and demographic info
names(dep_status) <- c('rownum', 'userid','time','text','other')
dep_status <- dep_status[c('userid','time','text')]
demog_selected <- demog[c('userid','gender','age')]
dep_status_demog <- merge(dep_status, demog_selected, by = 'userid', all.x = T)
unique_users <- dep_status_demog[!duplicated(dep_status_demog$userid),]
```

Here we select users who completed CES-D survey, with demographic information and fb status updates. There are `r dim(dep)[1]` participants completed CES-D, these users posted `r dim(dep_status)[1]` status updates from Jan 2009 - Nov 2011. `r dim(demog)[1]` users also have demographic info, eventually we idenfity `r dim(unique_users)[1]` users completed cesd, have demographic info and status updates.

#recode depression score
CESD NOTE: -1 means “user submitted a form with that question in but left it blank”, 0 means “user didn't submit a form with that question in” and 1, 2, 3, 4 are the response options.
here we need to remove participants with -1 and 0

```{r}

clean_dep <- function(dep_data) {
  for (i in 8:27){
    dep_clean <- dep_data[!dep_data[i] == -1, ]
    dep_data <- dep_clean
    return (dep_data)
  }
}

dep_clean <- clean_dep(dep)
```

## demographic info
```{r}
#merging data
all_info <- merge(unique_users, dep, by = 'userid', all.x =T)
all_info <- all_info[!duplicated(all_info$userid),]
all_info$time <- NULL
all_info$text <- NULL
#write.csv(all_info,'\data\unique_user_info.csv')
```

##age
```{r demographic, include=FALSE}
minor <- all_info[all_info$age < 18, ]
final_participants <- all_info[all_info$age >= 18, ]
```

Among `r dim(unique_users)[1]`  users, `r dim(minor)[1]`  of them were lower than 18 years old, we remove these participants and yeild `r dim(final_participants)[1]` participants. Here we show their demographic infomation

### gender
```{r gender, include=TRUE}
table(final_participants$gender)
prop.table(table(final_participants$gender))
```

### age
```{r, include=TRUE}
summary(final_participants$age)
```

### ethnicity
```{r gender, include=TRUE}
table(final_participants$ethnicity)
prop.table(table(final_participants$ethnicity))
```

### maritual status
```{r gender, include=TRUE}
table(final_participants$marital_status)
prop.table(table(final_participants$marital_status))
```

## Depression score
CESD NOTE: -1 means “user submitted a form with that question in but left it blank”, 0 means “user didn't submit a form with that question in” and 1, 2, 3, 4 are the response options.
here we need to remove participants with -1 and 0
```{r gender, include=TRUE}


final_participants$cesd_sum <- rowSums(final_participants[10:29])
summary(final_participants$cesd_sum)
```
Here we visualise their depression symptom score

```{r , echo=FALSE}
plot(pressure)

p <- ggplot(SelData) +
    geom_density(aes(x=CESD_sum), fill="#ADD8E6", size=1) +
    labs(title="CESD Score") +
    theme(text = element_text(size=20))+
    xlim(-10,60) +
    xlab("Normal Dist. mean=23.79, sd=12") +
    ylab("Density") +
    geom_vline(xintercept=22, linetype="longdash", colour="red") +
    annotate("text", x=0, y=0.02, label= "low score", size = 6) +
    annotate("text", x = 50, y=0.02, label= "high score", size = 6) 
p
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
