---
title: "select_data"
author: "Lushi Chen"
date: "21 October 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(lubridate)
require(ggplot2)
require(openair)
```

## data selection
### Here we selected frequent users for our prediction model, frequent users refer to those who posted at least once per week for half the year

*Maria's note: the way you've written it means that they have posted at least once in a time period of 25 weeks. I recommend using 26 weeks as your unit, because that is exactly half the year.*

```{r stats, include=FALSE}
path = '/home/lucia/phd_work/mypersonality_data/predicting_depression_symptoms/data/'
setwd(path)
participants <- read.csv('participants_matched.csv')
status <- read.csv('status_sentiment.csv')
```
```{r merge, include=FALSE}
participants_b <- participants[,c('userid', 'time_completed','cesd_sum')]
sel_status <- merge(participants_b, status, by = 'userid')
sel_status$X <- NULL
#all$time_diff <- difftime(as.Date(all$date_added_CESD), as.Date(all$post_time) , units = c("days"))
```

*Q from Maria: what is the content of the participants\_matched file?*

Here we show the posting statistics, there are `r dim(sel_status)[1]` posts from  `r dim(participants_b)[1]` users (y 2009 - y 2012). We can see that ppl posted more often in 2010

```{r, echo=FALSE}
#convert to date object
sel_status$time <- as.Date(sel_status$time)
count_tab <- data.frame(table(sel_status$time))
count_tab$Var1<- as.Date(count_tab$Var1)

ggplot(data = count_tab , aes(x = Var1, y = Freq))+
  geom_line(color = "#00AFBB", size = 2)
```

*Q from Maria: what are the names and units of the axes? What are the units of the time axis? Days/weeks?*

```{r week, include=FALSE}
#get week
sel_status$week<- week(sel_status$time)
#divided data in year
get_frequent_user <- function(year) {
  sel_status2009 <- subset(sel_status, format(as.Date(time),"%Y")==year)
  #group data by userid, week, then count number of posts each week
  sel_status2009$count <- 1
  week_count <- aggregate(count ~userid+week, data=sel_status2009, sum, na.rm=TRUE)
  #There are 52 weeks in a year, let's see for each participants, how many weeks do they have at least one post
  week_stats2009 <- as.data.frame(table(week_count$userid, week_count$week))
  week_has_post <- aggregate(Freq ~Var1, data=week_stats2009, sum, na.rm=TRUE)
  #select those has post in at least 25 weeks 
  frequent_user <- week_has_post[week_has_post$Freq >= 25,]
  return (frequent_user)
}

frequent_user2009 <- get_frequent_user(2009)
frequent_user2010 <- get_frequent_user(2010)
frequent_user2011 <- get_frequent_user(2011)

frequent_users <- rbind(frequent_user2009, frequent_user2010)
frequent_users <- rbind(frequent_users, frequent_user2011)
#write.csv(frequent_users, 'frequent_users.csv')
```

We see the number of posts a user write in each week and we selected `r dim(frequent_users)[1]` users who wrote at least 1 post in 25 weeks in a year (52-53 weeks). week_stats2009 shows whether user has at least one post each week 

*Q from Maria: Can you please show those statistics in the file? the path points to your home directory, not to a shared OneDrive or DataSync*

